Regime transition identification for basin's governance challenges of water use

### 2020-11-10 tex/main/manuscript.tex
update introduction gov.

\label{introduction-section-2}
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts 
\cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 人水系统中的水资源功能
Water have several key functions within a human-water system, the most important of which is sustaining the development of human societies through water utilization. 
% 水资源利用 regime shift
However, interplayed human interference, such as water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
\cite{falkenmarkUnderstandingWaterResilience2019}.
% 稳态转换随着社会发展增加
These gradual or abrupt changes triggered regime shifts as societies' development strengthen their interlinks to water utilization with increased dependences.
% TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
% Regime 过渡性的存在
As a result, most large river basins had gone through phases of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern in water utilization. 
% TODO 这里需要安排参考文献，大河流域的发展历程
% 因此，识别水资源利用的稳态变化，并从中寻找一般性的发展模式，有助于理解流域存在的问题
Identifying the regime shifts in water utilization and sketching a general pattern, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.

% 这里删掉的部分
% % 过渡性有助于理解流域存在的问题
% Sketching the transition of water utilization regimes, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
% % 对过渡性的研究还很少
% Despite pervasiveness, there is still lacking of effective method to distinguish the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transitions as well.

% Tag 引言第三段
% 前人已经从不同维度刻画了人水关系.
Features of water utilization has been depicted and studied from various intertwined perspectives.
% 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
Firstly, water stresses are of increasing importance and concerns.
Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use, while store of water resource in reservoirs are helpful to relief of
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
Secondly, as the priority of water utilization changed with the need of development. 
There are noticeable growths in economy profits of industry or services and their priority in water use, leading potential conflicts between different sectors
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
Thirdly, since development are inherently regional concerns, where heterogeneous regions attempt to develop themselves by economically competitive sectors, configuration of water resources also plays as an important aspect.
% 全球总的取水量很少，但缺水地区很多
% As a result, while only 10\% of available water is withdrawn on global average, about 30\% of population settles in severe water-stressed regions for higher level of development
% \cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
% 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
Taken together, existing researches have evaluated the three dimensions of water resource utilization regarding a series of crucial questions: ``How much water resources?'', ``How to use them?'' and ``Used for whom or in where?''.
% 将三种视角结合，就是“水资源利用体系”。
However, these dimensions haven't been well integrated by quantitative methods, and a coherent interpret of regime shifts regard to social development and water utilization is needed.

% tag 引言最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization (Figure~\ref{fig:framework}).
% 使用案例研究
Then, by applying this index to the Yellow River Basin, China, we analysed water utilization regimes shifts and their drivers in this typical basin of anthropogenic impacts.
% 最后总结出一般性框架
Finally, we proposed a transition phases framework of development echoing to the regime shifts, which can be a useful guideline for basins to predict dilemmas in water utilization and to develop in a coordinated way.

>>>>

\label{introduction-section-2}
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts 
\cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 因此，识别水治理的制度变迁对于快速变化的流域具有重要意义，可以作为水利用的系统转变的信号，并给可持续发展带来新的挑战。
Therefore, identifying regime shifts of water governance is important for fast-changing river basins, since it can be a signal of substantive change in water use and lead to new challenges in sustainability at a basin scale.
% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
According to United Nations Development Programme (UNDP), three key aspects of water use are decided by water governance: ``How to meet scarcity of water use? (stress of water use)'', ``How to balances different water use services? (provision of water use)'' and ``How to allocate water equally and efficiently? (allocation of water use)''.
% 这三个问题的答案取决于不同水治理制度下的环境、经济、社会和政治形势。
Answers of the three questions depend on environmental, economic, social and political situation within different water governance regimes. 
% 首先，受环境恶化和经济发展用水的影响，水资源短缺会增加社会的压力，但水库建设等管理政策有助于缓解压力。
Firstly, effected by environment deteriorate and water uses for economic development, water scarcity can increase stress on society, but management policies such as construction of reservoirs are helpful to relief the stresses.
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
Secondly, there is trade-off between provisioning water use (such as domestic use and food production uses) and non-provisioning water (such as uses for industrial production or energy), which in need of considerations through water governance
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
Thirdly, since allocation is basins' concerns, it not only influenced by regional environmental foundations, but also changed by regions' economic comparative advantages, which may effected by social development and policies.
% 总的来说，用水治理决定了与用水的“压力”、“供给”和“分配”，而三者在用水转向社会-水循环的过程中都发生着不断的变化
In general, water governance determines the ``stresses'', ``provision'' and ``allocation'' of water use, which all change constantly in the transformation towards the hydro-social water cycle because of changes environmental, economic, social and political situation Figure~\ref{fig:framework}.
% 因此，通过识别这种变化的稳态转化对理解是很有帮助的。
Therefore, identification of regime shifts for water governance is critical to understand the complex changes of relationships between human societies and water use.

% 黄河流域(YRB，见\textit{ Appendix}方法S1)，在中国经历了最激烈的水资源开发和最剧烈的管理制度变化。
The Yellow River Basin (YRB, see \textit{Appendix} Methods S1) had experienced the most intense water exploitation and the most dramatic shifts of management regime in China. 
% 从古至今，黄河一直为水治理带来了异乎寻常的挑战
Since ancient times, YRB had brought extraordinary challenges to water governance.
% 对1960年以前的中国，黄河巨大的含沙量不仅给YRB带来了洪泛灾害，更为利水带来巨大困难。
Before 1960, the huge sediment loads of the Yellow River in China not only brought flood disasters, but also brought great difficulties to water use of YRB. 
% 随着水保措施、水库调水调沙、修堤等治理措施的落实才得到了有效遏制。
With the implementation of governance measures such as conservation policies, regulation reservoirs, and levees constructions, these issues were effectively contained.
% 但随之而来的是越来越严重的断流，为水治理带来了新的挑战。 
However, more and more serious drying up of the Yellow River brings new challenges to governance and promoted a range of related policies to deal with.
% 如今，黄河流域仍面临严峻的治理挑战，因为区域的用水需求仍很难被全盘满足，而必须做出权衡。
Today, the Yellow River basin still faces serious governance challenges, as regional water demands are still difficult to be fully met and various trade-offs must be involved.
% 总之，随着人类影响逐步加大，为了应对层出不穷的治理挑战，黄河流域水治理发生的迅猛转变堪称世界之最。
All in all, the transformation of the Yellow River basin has been the most rapid in the world in response to the endless governance challenges brought by the increasing human influence.
% 因此如果能理解黄河水治理稳态的转换过程，其模式能为世界大河流域用水的可持续提供见解。
Therefore, identifying the regime shifts of water governance for YRB can provide key insights for the sustainable water use governance in the world's great river basins.

% tag 引言最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, by integrating three above mentioned key questions in water governance, we develop an Integrated Water Governance Index (IWGI) at a basin scale to indicate changes of basin's water governance (Figure~\ref{fig:framework}).
% 使用案例研究
Then, by applying this index to the YRB, we analysed the regimes shifts of water governance and their main causes, in this typical basin of rapidly transforming.
% 最后总结出一般性框架
Finally, we summarized a general regime transition schema, echoing to the different challenges in water governance, which can be a useful guideline for basins to develop in a coordinated way.
